Papers

### 2023-08-29 quarto/index.qmd
update

Hi! I'm happy to connect and discuss. Our office is at <a href="https://www.google.com/maps/place/2795+Augustine+Dr,+Santa+Clara,+CA+95054/@37.3835062,-121.9778599,17z/data=!3m1!4b1!4m5!3m4!1s0x808fc9f208b94da1:0xd2df9ae053c51af0!8m2!3d37.383502!4d-121.9756659" target="_blank">Santa Clara</a> in the San Francisco Bay Area. Just email me.

@@

>>>>

@@

* C. Qin, **A. Zhang**, Z. Zhang, J. Chen, M. Yasunaga, and D. Yang<br>
<a href="https://arxiv.org/abs/2302.06476" target="_blank">Is ChatGPT a General-Purpose Natural Language Processing Task Solver?</a><br>
*"Can ChatGPT solve, for example, sequence tagging?"*
In *arXiv*, 2023<br>
